\documentclass[a4paper,twocolumn]{memoir}

\usepackage{gurps}
\usepackage{multicol}
\usepackage{xparse}
\usepackage{xspace}

\NewDocumentCommand{\jhop}{}{\textsf{JHop}\xspace}
\NewDocumentCommand{\source}{}{\textsf{Source}\xspace}

\title{JHop\thanks{\SJGamesOnlinePolicyGameAid{Nathanael Farley} All work herein
  is under CC-BY-NC-SA v4.0.}}
% TODO get a proper licence section
\begin{document}
\maketitle


\chapter{Setting}
\label{cha:setting}
% TODO make this a beautiful single column centered start to the chapter.
\textit{The stars shone as they did every day on JHop. The terran colony had existed
  this way for as long as anyone could remember. Christmas time was in the air as
  jazz-hop music played from every store speaker. People went about their shopping
  at all hours; with no Sun to guide them and no assistants needed at
  old-fashioned checkouts, there was no closing time.}

\jhop is a small moon colony deep in space. Mostly self-sufficient, it's main
source of heat is from background radtion. Too far away from it's parent star to
use as a useful night and day, the hours roll by and people work in shifts all
the time. There's a 22 hour rest period where all non-essential work stops where
people shop and hang out with friends. But apart from that, it's hard work on
this capatilist colony.

\section{Currency}
\label{sec:currency}

When the colonists arrived some time ago, they were all given nanites which
provided an extra-sensory experience by applying pressure to different parts of
the body. Soon after landing, (or before, no-one quite knows,) this
\emph{nanosense} was assigned to individual currency amounts. Since the nanites
are self replicating, children are given nanites by their mother in the womb. At
birth the nanites are programmed to represent the newly birthed individual along
with the newly created records. (If this did not happen, the currency of the
mother stay linked to the child, in effect tying mother and daughter/son
together such that they are one person. Obviously this is illegal.)

When the individual spent money, they felt it `leave' them. When they went into
debt, they felt a real pain. For the super rich, this leaving feeling was very
subtle, but for those on the breadline, it was unmistakeable. There is very
little debt, because it \emph{hurts} to be in debt. For those who are
unfortunate enough to be in debt, the pain is with them forever until they
become solvent again. The worse the debt, the worse the pain\footnote{a true
  gangsta's paradise}.

Since all currency is represented by nanites, people can walk into stores and
take what they want off the shelf and it's charged as they leave. If they picked
it up and took it off the shelf, they are charged. (It is possible to link your
currency with other's nanites for a temporary period for this purpose.)

\section{Food}
\label{sec:food}

No sun means no sunlight. Vegetation is rare on \jhop, with most power and food
provided by a species of moss named \source. It's often flavoured with old Earth
flavouring like chicken or mince pies.

When \source is freshly grown, it has a slight glow to it. This glow quickly
disappears when the produce is processed/cooked.
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
