\documentclass[a4paper,twocolumn,oneside]{memoir}

\usepackage{gurps}
\usepackage{libertine}
\usepackage{microtype}
\usepackage{xparse}
\renewcommand{\familydefault}{\sfdefault}

\setulmarginsandblock{1.5cm}{1.5cm}{*}
\setlrmarginsandblock{1.5cm}{1.5cm}{*}
\checkandfixthelayout

\setsecnumdepth{subsubsection}

% Useful macros
\NewDocumentCommand{\system}{m}{\textsc{System#1}}
\NewDocumentCommand{\player}{m}{\textbf{\mbox{#1}}}

\title{\system{51} source book}
\author{Nathanael~Farley, David~Sumner, et al.}

\begin{document}

\part{General information}
\label{part:general-information}

\chapter{History}
\label{cha:history}

\section{Nanite wars}
\label{sec:nanite-wars}

They never intended to hurt anyone. They never intended anything. They were just dumb 
machines, the same way ants are \emph{just} dumb insects. Ships turned into dust.
The nanites just wanted to multiply, like some terrible virus. Maybe it was a joke
by a cruel universe for playing powers we were not meant to have.

No-one knows quite how it started. Perhaps there were ghosts in the code; unintended
consequences of errant lines of code. Maybe someone thought it would be good to help
them reproduce. Either way, they spread before we could do anything about it. They
adapted to all our measures as if \ldots{}. On their own, each nanite was harmless
but as a whole they became something much more deadly. Just as ants group together
to cross the river the nanties bound together to \emph{consume}.

\begin{itemize}
\item Worlds left desolate
\item \system{37} was abandoned during the wars with resources for the planets depleted
\item Rumours of patches of dormant nanites, floating in space, waiting for
  enough energy to do something
\item Since then, nanites have been banned. Even the bad guy stay away from them
\item This was all 1000~years ago. And people still remember. That's how bad it was
\end{itemize}

\part{GM's cubby corner}
\label{part:gms-cubby-corner}


\chapter{Adventure prep}
\label{cha:adventure-prep}

\section{Session 1}

\subsection{Hooks}
\label{sec:hooks}

\subsubsection{The angry boss}
\label{sec:angry-boss}

\paragraph{Basic idea}

Players are told beforehand that something is going to happen and they are going
to have to improv. Whatever they say will be accepted as true (or a lie if they
want). The characters then enter a room where the boss shouts ``What the hell
happened? You killed the wrong guy!'' \emph{Cue improv.}

\paragraph{Pros}

\begin{itemize}
\item Don't need to know much about the characters
\item Shows people's colours quickly
\end{itemize}

\paragraph{Cons}

\begin{itemize}
\item Doesn't lead anywhere by default
\end{itemize}


\subsubsection{The job}
\label{sec:job}

\paragraph{Basic idea}

The team get given a job, Charlie's Angels style: rob a mafia bank. Payout is
given \emph{on delivery} but only a certain amount must be stolen (client's
wishes). If more is stolen the team will be in trouble.

\paragraph{Pros}

\begin{itemize}
\item \player{Matt K.} will totally steal more
\item Can split the party to go information searching
  \begin{itemize}
  \item This even means that David and I can find different information and
    combine it (making more improv.\ excellency)
  \end{itemize}
\end{itemize}

\paragraph{Cons}

Will have to prep a building for everyone to get involved in. Basically design
an entire challenge.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
